Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-03 latex/robdml.tex
tex

% contributions
%In brief, our contribusions include:
In this MLSP project, we plan to make the following contributions:
%
\begin{enumerate}[noitemsep]
	%
	\item {\textit{Hardness Manipulation}} is proposed for the adversarial
		training of triplet-based deep metric learning models, which avoids
		model collapse in the typical min-max adversarial training setting.
		The proposed method achieves higher adversarial robustness compared to
		the state-of-the-art, and is more computationally efficient.
		%
	\item \textit{Gradual Adversary} is proposed to dynamically adjust the
		destination hardness less for Hardness Manipulation during the
		adversarial training process in order to balance the metric learning
		and adversarial learning.
		%
	\item Revise and incorporate the state-of-the-art adversarial training
		acceleration method (\ie, Free Adversarial Training~\cite{freeat},
		which is designed for classification) into adversarial training of 
		deep metric learning models. It will greatly improve the efficiency
		of adversarial training.
		%
	\item Benchmark of existing metric learning loss functions under
		adversarial training scenario, and analyze their different
		characteristics for future reference.
		%
	\item Explore the possibility of proposing a new metric learning loss
		function oriented for adversarial training, starting from scratch or
		from an existing metric learning loss.
		%
\end{enumerate}

>>>>

% contributions
%In brief, our contribusions include:
In this MLSP project, we plan to make the following contributions:
%
\begin{enumerate}[noitemsep]
	%
	\item {\textit{Hardness Manipulation}} is proposed for the adversarial
		training of triplet-based deep metric learning models, which avoids
		model collapse in the typical min-max adversarial training setting.
		The proposed method achieves higher adversarial robustness compared to
		the state-of-the-art, and is more computationally efficient.
		%
		This method makes min-max training feaisble, and hence the incorporation
		into free adversarial training and boost learning efficiency.
		%
		(initial condition)
		%
	\item \textit{Gradual Adversary} is proposed to dynamically adjust the
		destination hardness less for Hardness Manipulation during the
		adversarial training process in order to balance the metric learning
		and adversarial learning.
		%
		(terminal condition)
		%
	\item Inter-ID structure constraint. ((aa~p) + (pp~a))/2
		(cross-id repelling)
		existing methods only care inter-class separation, but not
		intra-class (inter-id) separation, because we may get a 6-element
		set (a,a~,p,p~,n,n~) from the original triplet.
		%
	\item Revise and incorporate the state-of-the-art adversarial training
		acceleration method (\ie, Free Adversarial Training~\cite{freeat},
		which is designed for classification) into adversarial training of 
		deep metric learning models. It will greatly improve the efficiency
		of adversarial training.
		%
	\item Benchmark of existing metric learning loss functions under
		adversarial training scenario, and analyze their different
		characteristics for future reference.
		%
	\item Explore the possibility of proposing a new metric learning loss
		function oriented for adversarial training, starting from scratch or
		from an existing metric learning loss.
		%
\end{enumerate}
